Paper Analyses

### 2023-03-01 ABCDModel.Rmd
Cleaned up code, added comments & rearranged sections, updated plotting code

Predict Brain Age (follow-up)
```{r}
brain_age_df_followup <-
  xgb_mod %>%
  predict(new_data = renamed_smri_followup) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = renamed_smri_followup$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)
```

Evaluate accuracy
```{r}
# compute common performance metrics: mae, rsq, rmse
brain_age_df_baseline %>%
  metrics(truth = truth, estimate = .pred)

brain_age_df_followup %>%
  metrics(truth = truth, estimate = .pred)
```

@@

#Follow-up
brain_age_corrected_df_followup <- brain_age_df_followup %>%
  mutate(
    # corrected brain age prediction
    corrected_pred =  (.pred - bias_intercept) / bias_slope
  ) %>%
  # corrected corrected brain age gap
  mutate(corrected_gap = corrected_pred - truth)

@@

brain_age_corrected_df_followup %>%
  metrics(truth = truth, estimate = corrected_pred)

@@

save(brain_age_df_followup, file="ABCDFollowUpBrainAge.Rda")
save(brain_age_corrected_df_followup, file="ABCDFollowUpBrainAgeCorrected.Rda")

>>>>

Predict Brain Age (follow-up)
(for future analyses, no current follow-model)
```{r, eval = F}
brain_age_df_followup <-
  xgb_mod %>%
  predict(new_data = renamed_smri_followup) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = renamed_smri_followup$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)
```

Evaluate accuracy
```{r}
# compute common performance metrics: mae, rsq, rmse
brain_age_df_baseline %>%
  metrics(truth = truth, estimate = .pred)
```

```{r, eval=F}
#brain_age_df_followup %>%
#  metrics(truth = truth, estimate = .pred)
```

@@

#Follow-up
#brain_age_corrected_df_followup <- brain_age_df_followup %>%
#  mutate(
    # corrected brain age prediction
#    corrected_pred =  (.pred - bias_intercept) / bias_slope
#  ) %>%
  # corrected corrected brain age gap
#  mutate(corrected_gap = corrected_pred - truth)

@@

#brain_age_corrected_df_followup %>%
#  metrics(truth = truth, estimate = corrected_pred)

@@

#save(brain_age_df_followup, file="ABCDFollowUpBrainAge.Rda")
#save(brain_age_corrected_df_followup, file="ABCDFollowUpBrainAgeCorrected.Rda")

### 2023-03-01 DataSetup.Rmd
Cleaned up code, added comments & rearranged sections, updated plotting code

Load Other Variables
```{r}
load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/BaselineBrainAgeCorrected.Rda")
load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/FollowUpBrainAgeCorrected.Rda")

#Puberty
#Raw scores, youth
youth_pds <- rio::import("/Volumes/devbrainlab/ABCD_Data/ABCD4pt0/abcd_ypdms01.txt") %>%
  filter(!collection_title=="collection_title") %>% 
  select(5:38) %>% 
  select(-c(interview_date, pds_remote___1, pds_remote___2, pds_remote___3, pds_remote___4, pds_device)) %>% 
  mutate_at(c(5:28), as.numeric)

@@

gish <- rio::import("/Volumes/devbrainlab/ABCD_Data/ABCD4pt0/abcd_gish2y01.txt") %>%
  filter(!collection_title=="collection_title")  %>% 
  filter(eventname == "2_year_follow_up_y_arm_1") %>% 
   select(src_subject_id, sex, contains("gish2")) %>% 
  select(-c(gish2_device, abcd_gish2y01_id))%>% 
  mutate_at(c(3:15), as.numeric)

@@

Add age to brainAGE estimates
```{r}
corrected_baseline_brainage <- brain_age_corrected_df_baseline
corrected_followup_brainage <- brain_age_corrected_df_followup

corrected_baseline_brainage$src_subject_id <- smri_baseline$src_subject_id

@@

#Add Gish to follow-up
```

Attach maturity variables to ABCD model estimates
```{r}
abcd_brainage_baseline <- rio::import("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/ABCDBaselineBrainAgeCorrected.Rda")
abcd_brainage_baseline$src_subject_id <- sample_2_baseline$src_subject_id

@@

#double check that sample 2s remain consistent

abcd_baseline_ids <- abcd_brainage_baseline$src_subject_id

@@

#smri_abcd_model_baseline <- renamed_smri_baseline[, 1:180]

>>>>

Load Other Variables
```{r}
#Puberty
#Raw scores, youth
youth_pds <- rio::import("/Volumes/devbrainlab/ABCD_Data/ABCD4pt0/abcd_ypdms01.txt") %>%
  filter(!collection_title=="collection_title") %>% 
  select(5:38) %>% 
  select(-c(interview_date, pds_remote___1, pds_remote___2, pds_remote___3, pds_remote___4, pds_device)) %>% 
  mutate_at(c(5:28), as.numeric)

@@

#gish <- rio::import("/Volumes/devbrainlab/ABCD_Data/ABCD4pt0/abcd_gish2y01.txt") %>%
#  filter(!collection_title=="collection_title")  %>% 
 # filter(eventname == "2_year_follow_up_y_arm_1") %>% 
#   select(src_subject_id, sex, contains("gish2")) %>% 
 # select(-c(gish2_device, abcd_gish2y01_id))%>% 
 # mutate_at(c(3:15), as.numeric)

@@

```
**At this point, switch to the ExistingModel.Rmd file, where you can use renamed_smri_baseline and renamed_smri_followup to make predictions.**

Add age to brainAGE estimates - Exisiting Model
```{r}
#Don't need to run the load lines if you just ran ExistingModel.Rmd, these will already be loaded
load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/BaselineBrainAgeCorrected.Rda")
load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/FollowUpBrainAgeCorrected.Rda")

#make renamed copies of predictions
corrected_baseline_brainage <- brain_age_corrected_df_baseline
corrected_followup_brainage <- brain_age_corrected_df_followup

#add subject ids to predictions
corrected_baseline_brainage$src_subject_id <- smri_baseline$src_subject_id

@@

#Add Gish to follow-up at a later date
```

#can run the line below if you need to reload smri_abcd_model_baseline
#smri_abcd_model_baseline <- renamed_smri_baseline[, 1:180]

**Switch over to ABCDModel.Rmd to get predictions from ABCD-trained model**

Attach maturity variables to ABCD model estimates
```{r}
#if you just ran ABCDModel.Rmd, comment out the next line
abcd_brainage_baseline <- rio::import("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/ABCDBaselineBrainAgeCorrected.Rda")
abcd_brainage_baseline$src_subject_id <- sample_2_baseline$src_subject_id

@@

#double check that sample 2s remain consistent
abcd_baseline_ids <- abcd_brainage_baseline$src_subject_id

@@

**Below section is for future analyses**

### 2023-03-01 PaperAnalyses&Figures.Rmd
Cleaned up code, added comments & rearranged sections, updated plotting code

abcd_brainage_baseline <- rio::import("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/ABCDBaselineBrainAgeCorrected.Rda")

@@

#load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/abcd_baseline.Rda")
load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/ABCDBaselineBrainAgeCorrected.Rda")

@@

  #join once by baseline IDs, then by follow-up (only recorded at one wave)

demographics_baseline <- left_join(brainage_pds_baseline, demographics)

@@

demographics_baseline_abcdmodel <- left_join(demographics_baseline_abcdmodel, demographics_long %>% filter(eventname == "baseline_year_1_arm_1"))

# Vlad's Model, Baseline Analyses

#Run Models
```{r}
# brainage ~ youth sum
#baseline_puberty_y_sum_1 <- lm(corrected_gap ~ youth_sum, data = sample_1)
#baseline_puberty_y_sum_2 <- lm(corrected_gap ~ youth_sum, data = sample_2)

@@

## Model Summaries
```{r}
summary(baseline_puberty_y_mean_1)
summary(baseline_puberty_y_mean_2)

@@

```
Model Summaries of Models w/ age as covariate
```{r}
summary(baseline_puberty_y_mean_1_m)
summary(baseline_puberty_y_mean_2_m)

@@

Figure 2
Use subsample, otherwise it’ll look super funky

Scatterplot of scan age/chronological age vs predicted age
2 panels: 1 for validation, 1 for analysis sample
1 or 2 extra panels for analysis sample w/ Vlad's model
```{r}
#subsample data
#sample_n()

baseline_pred_mod1_plot <- ggplot(brainage_pds_baseline, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#A1C181")+
  geom_abline(a=0, b=1, color='#233D4D') +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="baseline_truth_corrected_pred_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

baseline_gap_mod1_plot <- ggplot(brainage_pds_baseline, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#A1C181")+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="baseline_truth_corrected_gap_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

```{r}
ggpar((corrected_baseline_brainage %>% 
  #filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", add="mean")), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Baseline")

@@

followup_pred_mod1_plot <- ggplot(brainage_pds_followup, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#619B8A")+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="followup_truth_corrected_pred_mod1.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
followup_gap_mod1_plot <- ggplot(brainage_pds_followup, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#619B8A")+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="followup_truth_corrected_gap_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

ggsave(filename = "pred_bias_mod1.png",
                          width=10, height=10, units='in', dpi=300)

#Fit Metrics

#baseline uncorrected
corrected_baseline_brainage %>%
  metrics(truth = truth, estimate = .pred)
#baseline corrected
corrected_baseline_brainage %>%
  metrics(truth = truth, estimate = corrected_pred)

@@

### Follow-Up Analyses

@@

##### ABCD Model #####

@@

Plots & Decriptives for ABCD Model
```{r}
describe(abcd_brainage_baseline)
#describe(abcd_brainage_baseline %>% filter(truth != 9))
#describe(abcd_brainage_baseline %>% filter(between(truth, 9, 9.2)))

@@

ggscatter(abcd_brainage_baseline, x = "truth", y = ".pred",
   color = "#00AFBB", # Points color, shape and size
   add = "reg.line",  # Add regressin line
   add.params = list(color = "blue", fill = "lightgray"), # Customize reg. line
   conf.int = TRUE # Add confidence interval
   )

@@

baseline_pred_mod2_plot <- ggplot(abcd_brainage_baseline, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#E76F51")+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
ggsave(filename="baseline_truth_corrected_pred_mod2.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
baseline_gap_mod2_plot <- ggplot(abcd_brainage_baseline, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#E76F51")+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
ggsave(filename="baseline_truth_corrected_gap_mod2.png",
                          width=7, height=4, units='in', dpi=300)

@@

#### ABCD Model - Baseline
```{r}
abcd_baseline_months <- abcd_baseline %>% 
  mutate(interview_age_m = interview_age/12)

@@

## Model Summaries
```{r}
summary(abcd_baseline_puberty_y_mean)

#summary(abcd_baseline_puberty_y_sum)

@@

#summary(abcd_baseline_puberty_p_sum)

#summary(abcd_baseline_cognition_crystal)

#summary(abcd_baseline_cognition_fluid)

@@

summary(abcd_baseline_cognition_standard)

```
Model Plots
```{r}
#Cognition
ggPredict(abcd_baseline_cognition_standard,se=TRUE)

@@

ABCD Baseline Model
```{r}
#Youth-Report Puberty
#make categorical variable for puberty
#age-corrected cognition: These are presented as Standard Scores (mean=100, SD=15).
abcd_baseline_categorical_pds <- abcd_baseline %>% 
  mutate(youth_pds_cat=cut(youth_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         parent_pds_cat=cut(parent_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         cognition_cat=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 85, 115, Inf), labels=c(">-1", "-1-1", ">1")),
         cognition_cat_small=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 92, 108, Inf), labels=c(">-.5", "-.5-.5", ">.5")),
         cog_quart = cut(nihtbx_totalcomp_uncorrected, quantile(nihtbx_totalcomp_uncorrected, na.rm=T), labels=c("0-25", "25-50", "50-75", "75-100")))

@@

###########
Combined Wave Model
###########
```{r}
#Fit Metrics
#baseline uncorrected
abcd_brainage_multiwave %>%
  metrics(truth = truth, estimate = .pred)
#baseline corrected
abcd_brainage_baseline  %>%
  metrics(truth = truth, estimate = corrected_pred)

>>>>

# ABCD Model Baseline BrainAGE estimates
abcd_brainage_baseline <- rio::import("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/ABCDBaselineBrainAgeCorrected.Rda")

@@

#load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/abcd_baseline.Rda")
#load("/Volumes/devbrainlab/Lucy/BrainAGE/fyp/ABCDBaselineBrainAgeCorrected.Rda")

@@

  #join once by baseline IDs, then by follow-up (only recorded at one wave)
demographics_baseline <- left_join(brainage_pds_baseline, demographics)

@@

demographics_baseline_abcdmodel <- left_join(demographics_baseline_abcdmodel, demographics_long %>% filter(eventname == "baseline_year_1_arm_1"))
```

**Vlad's Model, Baseline Analyses**
Run Models
```{r}
# brainage ~ youth sum
#baseline_puberty_y_sum_1 <- lm(corrected_gap ~ youth_sum, data = sample_1)
#baseline_puberty_y_sum_2 <- lm(corrected_gap ~ youth_sum, data = sample_2)

@@

Model Summaries
```{r}
summary(baseline_puberty_y_mean_1)
summary(baseline_puberty_y_mean_2)

@@

Model Summaries of Models w/ age as covariate
```{r}
summary(baseline_puberty_y_mean_1_m)
summary(baseline_puberty_y_mean_2_m)

@@

Figure 2
Scatterplot of scan age/chronological age vs predicted age
2 panels: 1 for validation, 1 for analysis sample
1 or 2 extra panels for analysis sample w/ Vlad's model
```{r}
#subsample data
#sample_n()

baseline_pred_mod1_plot <- ggplot(brainage_pds_baseline, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#A1C181", alpha=.2) +
  geom_abline(a=0, b=1, color='#233D4D') +
  #geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="baseline_truth_corrected_pred_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

baseline_gap_mod1_plot <- ggplot(brainage_pds_baseline, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#A1C181", alpha=.2)+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="baseline_truth_corrected_gap_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

Plots
```{r}
ggpar((corrected_baseline_brainage %>% 
  #filter(!is.na(youth_pds_cat)) %>% 
  ggdensity(x = "corrected_gap", add="mean")), 
  xlab="Brain Age Gap", ylab="Density", legend.title = "Baseline")

@@

followup_pred_mod1_plot <- ggplot(brainage_pds_followup, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#619B8A", alpha=.2)+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="followup_truth_corrected_pred_mod1.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
followup_gap_mod1_plot <- ggplot(brainage_pds_followup, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#619B8A", alpha=.2)+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 14))  
ggsave(filename="followup_truth_corrected_gap_mod1.png",
                          width=7, height=4, units='in', dpi=300)

@@

ggsave(filename = "pred_bias_mod1.png",
                          width=10, height=10, units='in', dpi=300)
```

Fit Metrics
```{r}
#baseline uncorrected
corrected_baseline_brainage %>%
  metrics(truth = truth, estimate = .pred)
#baseline corrected
corrected_baseline_brainage %>%
  metrics(truth = truth, estimate = corrected_pred)

@@

# Correlation between gap and age
cor(brainage_pds_baseline$truth, brainage_pds_baseline$corrected_gap)
cor(brainage_pds_followup$truth, brainage_pds_followup$corrected_gap)
```

**Follow-Up Analyses**

@@

**ABCD Model**

@@

Plots & Descriptives for ABCD Model
```{r}
describe(abcd_brainage_baseline)
#describe(abcd_brainage_baseline %>% filter(truth != 9))
#describe(abcd_brainage_baseline %>% filter(between(truth, 9, 9.2)))

@@

# Check age v gap
cor(abcd_baseline$truth, abcd_baseline$corrected_gap)

# Plots
ggscatter(abcd_brainage_baseline, x = "truth", y = ".pred",
   color = "#00AFBB", # Points color, shape and size
   add = "reg.line",  # Add regressin line
   add.params = list(color = "blue", fill = "lightgray"), # Customize reg. line
   conf.int = TRUE # Add confidence interval
   )

@@

baseline_pred_mod2_plot <- ggplot(abcd_baseline, aes(x=truth, y=corrected_pred)) + 
  geom_jitter(color="#E76F51", alpha=.25)+
  geom_abline(a=0, b=1, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Predicted Age") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
ggsave(filename="baseline_truth_corrected_pred_mod2.png",
                          width=7, height=4, units='in', dpi=300)

# Age Bias - truth vs corrected gap
baseline_gap_mod2_plot <- ggplot(abcd_baseline, aes(x=truth, y=corrected_gap)) + 
  geom_jitter(color="#E76F51", alpha=.25)+
  geom_smooth(method=lm, color='#233D4D') +
  labs(x = "Scan/Chronological Age", y ="Corrected Gap") +
  theme_classic() + 
  theme(text = element_text(size = 12))  
ggsave(filename="baseline_truth_corrected_gap_mod2.png",
                          width=7, height=4, units='in', dpi=300)

@@

ABCD Model - Baseline
```{r}
abcd_baseline_months <- abcd_baseline %>% 
  mutate(interview_age_m = interview_age/12)

@@

Model Summaries
```{r}
summary(abcd_baseline_puberty_y_mean)

@@

@@

summary(abcd_baseline_cognition_standard)
```
Model Plots
```{r}
#Cognition
ggPredict(abcd_baseline_cognition_standard,se=TRUE)

@@

ABCD Baseline Model - Density Plots
```{r}
#Youth-Report Puberty
#make categorical variable for puberty
#age-corrected cognition: These are presented as Standard Scores (mean=100, SD=15).
abcd_baseline_categorical_pds <- abcd_baseline %>% 
  mutate(youth_pds_cat=cut(youth_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         parent_pds_cat=cut(parent_mean, breaks=c(-Inf, 1, 2, 3, Inf), labels=c("1","2","3", "4")),
         cognition_cat=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 85, 115, Inf), labels=c(">-1", "-1-1", ">1")),
         cognition_cat_small=cut(nihtbx_totalcomp_uncorrected, breaks=c(-Inf, 92, 108, Inf), labels=c(">-.5", "-.5-.5", ">.5")),
         cog_quart = cut(nihtbx_totalcomp_uncorrected, quantile(nihtbx_totalcomp_uncorrected, na.rm=T), labels=c("0-25", "25-50", "50-75", "75-100")))

@@

Checking internal consistency of puberty means
```{r}
#Puberty
#Raw scores, youth
youth_pds <- rio::import("/Volumes/devbrainlab/ABCD_Data/ABCD4pt0/abcd_ypdms01.txt") %>%
  filter(!collection_title=="collection_title") %>% 
  select(5:38) %>% 
  select(-c(interview_date, pds_remote___1, pds_remote___2, pds_remote___3, pds_remote___4, pds_device)) %>% 
  mutate_at(c(5:28), as.numeric)

#Raw scores, parent
parent_pds <- rio::import("/Volumes/devbrainlab/ABCD_Data/ABCD4pt0/abcd_ppdms01.txt") %>%
  filter(!collection_title=="collection_title")  %>% 
  select(5:27) %>% 
  select(-c(interview_date, pds_select_language___1)) %>% 
  mutate_at(c(5:21), as.numeric)

#two or more missing values = exclude
#PDS mean score is a continuous value calculated by averaging across PDS items following Herting et al. (2021). Items on the PDS were considered missing if participants answered, “I don’t know” or “refuse to answer”, if the response was left blank, or if the response value was outside of the expected range (1 to 4). Participants with two or more missing answers were excluded from the PDS score calculation (following recommendations from (Herting et al., 2021)

### Youth-report, removes everyone w/o complete data
youth_pds[youth_pds == 777] <- NA
youth_pds[youth_pds == 999] <- NA

#### Parent-report, removes everyone w/o complete data
parent_pds[parent_pds == 777] <- NA
parent_pds[parent_pds == 999] <- NA

# Calculting internal consistency
# Use alpha output

# Baseline, youth-report, male
youth_pds %>% 
  #filter for baseline wave, male, has BrainAGE estimate
  filter(eventname == "baseline_year_1_arm_1", sex == "M", src_subject_id %in% brainage_pds_baseline$src_subject_id) %>% 
  #select values being used for mean calculation (male)
  select(c("pds_ht2_y", "pds_bdyhair_y", "pds_skin2_y","pds_m4_y","pds_m5_y")) %>% 
  psych::omega(nfactors=3)

# Baseline, youth-report, female
youth_pds %>% 
  #filter for baseline wave, female, has BrainAGE estimate
  filter(eventname == "baseline_year_1_arm_1", sex == "F", src_subject_id %in% brainage_pds_baseline$src_subject_id) %>% 
  #select values being used for mean calculation (male)
  select(c("pds_ht2_y", "pds_bdyhair_y", "pds_skin2_y","pds_f4_2_y","pds_f5_y")) %>% 
  psych::omega(nfactors=3)

# Baseline, parent-report, male                           
parent_pds %>% 
  #filter for baseline wave, male, has BrainAGE estimate
  filter(eventname == "baseline_year_1_arm_1", sex == "M", src_subject_id %in% brainage_pds_baseline$src_subject_id) %>% 
  #select values being used for mean calculation (male)
  select(c("pds_1_p", "pds_2_p", "pds_3_p", "pds_m4_p", "pds_m5_p")) %>% 
  psych::omega(nfactors=3)

# Baseline, parent-report, female                           
parent_pds %>% 
  #filter for baseline wave, female, has BrainAGE estimate
  filter(eventname == "baseline_year_1_arm_1", sex == "F", src_subject_id %in% brainage_pds_baseline$src_subject_id) %>% 
  #select values being used for mean calculation (male)
  select(c("pds_1_p", "pds_2_p", "pds_3_p", "pds_f4_p", "pds_f5b_p")) %>% 
  psych::omega(nfactors=3)

# Follow-up, youth-report, male
youth_pds %>% 
  #filter for baseline wave, male, has BrainAGE estimate
  filter(eventname == "2_year_follow_up_y_arm_1", sex == "M", src_subject_id %in% brainage_pds_baseline$src_subject_id) %>% 
  #select values being used for mean calculation (male)
  select(c("pds_ht2_y", "pds_bdyhair_y", "pds_skin2_y","pds_m4_y","pds_m5_y")) %>% 
  psych::omega(nfactors=3)

# Follow-up, youth-report, female
youth_pds %>% 
  #filter for baseline wave, female, has BrainAGE estimate
  filter(eventname == "2_year_follow_up_y_arm_1", sex == "F", src_subject_id %in% brainage_pds_baseline$src_subject_id) %>% 
  #select values being used for mean calculation (male)
  select(c("pds_ht2_y", "pds_bdyhair_y", "pds_skin2_y","pds_f4_2_y","pds_f5_y")) %>% 
  psych::omega(nfactors=3)

# Follow-up, parent-report, male                           
parent_pds %>% 
  #filter for baseline wave, male, has BrainAGE estimate
  filter(eventname == "2_year_follow_up_y_arm_1", sex == "M", src_subject_id %in% brainage_pds_baseline$src_subject_id) %>% 
  #select values being used for mean calculation (male)
  select(c("pds_1_p", "pds_2_p", "pds_3_p", "pds_m4_p", "pds_m5_p")) %>% 
  psych::omega(nfactors=3)

# Follow-up, parent-report, female                           
parent_pds %>% 
  #filter for baseline wave, female, has BrainAGE estimate
  filter(eventname == "2_year_follow_up_y_arm_1", sex == "F", src_subject_id %in% brainage_pds_baseline$src_subject_id) %>% 
  #select values being used for mean calculation (male)
  select(c("pds_1_p", "pds_2_p", "pds_3_p", "pds_f4_p", "pds_f5b_p")) %>% 
  psych::omega(nfactors=3)

Check correlation between youth and parent report puberty
```{r}
# baseline youth & parent report
cor(brainage_pds_baseline$youth_mean, brainage_pds_baseline$parent_mean, use="complete.obs")

# follow-up youth and parent report
cor(brainage_pds_followup$youth_mean, brainage_pds_followup$parent_mean, use="complete.obs")

# abcd model baseline
cor(abcd_baseline$youth_mean, abcd_baseline$parent_mean, use="complete.obs")

**Combined Wave Model**

```{r}
#Fit Metrics
#baseline uncorrected
abcd_brainage_multiwave %>%
  metrics(truth = truth, estimate = .pred)
#baseline corrected
abcd_brainage_baseline  %>%
  metrics(truth = truth, estimate = corrected_pred)
